Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 Moltres.tex
incorporates review of Aufiero, Laureau, and Fiorina.

\gls{MSR} modeling efforts describe steady-state and
transient behavior. Krepel et al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR against
experimental \gls{MSRE} data and then used it to simulate local fuel channel
blockages as well as local temperature perturbations. In a similar vein, Kophazi
et. al. used iterative coupling between in-house three-dimensional neutronic and
one-dimensional heat conduction models DALTON and THERM to analyze normal 
\gls{MSRE} operation as well as channel-blocking-incident
transients \cite{kophazi_development_2009}. The Kophazi model added entrance 
effects of heat transfer coefficients as well as thermal
coupling between fuel channels through moderator heat conduction. More recently,
Cammi et. al. performed a 2D-axisymmetric single-channel analysis of the
\gls{MSBR} using the commercial finite element package COMSOL
Multiphysics \cite{cammi_multi-physics_2011}. That work directly solved the 
fuel salt velocity field, used heterogeneous group constants
in fuel and moderator regions, and employed a software package (COMSOL)
intrinsically designed for coupled multi-physics simulation.
Additionally, Aufiero et. al \cite{aufiero_development_2014} have begun to 
approach transient simulations in the \gls{MSFR} by directly coupling Serpent 2 
Monte Carlo neutronics with OpenFOAM \cite{weller_tensorial_1998} thermal-hydraulics.

>>>>

\gls{MSR} modeling efforts describe steady-state and
transient behavior. Krepel et al. extended the in-house \gls{LWR}
diffusion code DYN3D to consider drift of delayed neutron precursors alongside
the reactor temperature profile, re-casting the extended code as
DYN3D-MSR \cite{krepel_dyn3d-msr_2007}. That work compared DYN3D-MSR against
experimental \gls{MSRE} data and then used it to simulate local fuel channel
blockages as well as local temperature perturbations.

In a similar vein, Kophazi et. al. used iterative coupling between in-house
three-dimensional neutronic and one-dimensional heat conduction models DALTON
and THERM to analyze normal \gls{MSRE} operation as well as
channel-blocking-incident transients \cite{kophazi_development_2009}. The
Kophazi model added entrance effects of heat transfer coefficients as well as
thermal coupling between fuel channels through moderator heat conduction. More
recently, Cammi et. al. performed a 2D-axisymmetric single-channel analysis of
the \gls{MSBR} using the commercial finite element package COMSOL Multiphysics
\cite{cammi_multi-physics_2011}. That work directly solved the fuel salt
velocity field, used heterogeneous group constants in fuel and moderator
regions, and employed the \gls{COMSOL} software package intrinsically designed
for coupled multi-physics simulation.  Fiorina, Lathouwers, and their
colleagues conducted a benchmarking exercise \cite{fiorina_modelling_2013} in
which this Politecnico di Milano approach was expanded to a multi-channel model
and compared to code from the University of Delft
\cite{de_zwaan_static_2007,van_der_linden_2012} based on the approach in
\cite{kophazi_development_2009}. These models showed good agreement for
accident transients in the \gls{MSFR}.

More recently, Aufiero et.  al \cite{aufiero_development_2014} have begun to
approach transient simulations in the \gls{MSFR} within the finite volume
OpenFOAM multiphysics toolkit\cite{weller_tensorial_1998}.  This approach
benefits from pre-implemented turbulence models availble in the OpenFOAM
library and captures the full-core three-dimensional geometry of the reactor
primary circuit.  OpenFOAM \gls{CFD} has additionally been shown by Laureau et
al. \cite{laureau_transient_2017} to couple well with Transient Fission Matrix
neutronics within the \gls{MSFR}.
